---
title: "2023-2024 WR Grades"
author: "Gavin Bulthuis"
date: "2024-03-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here are my SNC WR grades for the 2023 - 2024 NFL season, I will use data from PFF and SumerSports to help in computing the grades.

\section {Data Loading}
Loading data and sorting WR's alphabetically (SumerSports data added to PFF data manually)
```{r}
#Load data
pff_csv <- read.csv("PFFWRDATA.csv")

#Sort players alphabetically
pff_csv <- pff_csv[order(pff_csv$player), ]
```

\section {Grade Calculations}

Coefficients and metrics used from PFF dataset
```{r}
#PFF model coefficients
pff_offense <- 0.185
total_epa <- 0.125
rating_rec <- 0.025
yac_rec <- 2.05
yprr <- 2.3
adot <- 0.27
cont_catch <- 0.14
targets_game <- 0.04
```

Calculating the SNC grade from PFF data
```{r warning=FALSE}
#Calculate pff model
for (player in seq_len(nrow(pff_csv))) {
  player_pff <- pff_offense * pff_csv$grades_offense[player]
  player_epa <- (total_epa * pff_csv$epa[player])
  player_rating_per_catch <- rating_rec * pff_csv$targeted_qb_rating[player]
  player_yac <- yac_rec * pff_csv$yards_after_catch_per_reception[player]
  player_yprr <- yprr * pff_csv$yprr[player]
  player_adot <- adot * pff_csv$avg_depth_of_target[player]
  player_cont_catch <- cont_catch * pff_csv$contested_catch_rate[player]
  player_targets <- (targets_game * pff_csv$targets[player])
  player_pffdata <- player_pff + player_epa + player_rating_per_catch + player_yac + player_yprr + player_adot + player_cont_catch + player_targets * 5
  pff_csv$player_total_pff[player] <- player_pffdata
}
write.csv(pff_csv, "PFFWRDATA.csv", row.names = FALSE)
```

\section {Conclusions}

Here are my top WR's based on this season alone from my SNC grade (the numbers next to players are their position in the spreadsheet and have no correlation to the players or the grade).
```{r}
pff_csv <- pff_csv[order(pff_csv$player_total_pff, decreasing = TRUE), ]
top <- head(pff_csv[,c("player", "player_total_pff")], 83)
print(top)
```