---
title: "QB SNC Grades"
author: "Gavin Bulthuis"
date: "2023-12-21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here are my SNC QB grades for the 2023 - 2024 NFL season, I will use data from PFF and RBSDM to help in computing the grades.

\section {Data Loading}
Loading data and sorting QB's alphabetically
```{r}
#Load data
pff_csv <- read.csv("PFFQBDATA.csv")
rbsdm_csv <- read.csv("RBSDMQBDATA.csv")

#Sort players alphabetically
pff_csv <- pff_csv[order(pff_csv$player), ]
rbsdm_csv <- rbsdm_csv[order(rbsdm_csv$Player), ]
```

\section {PFF Grade Calculations}

Coefficients and metrics used from PFF dataset
```{r}
#PFF model coefficients
btt_pct <- 0.075
twp_pct <- -0.05
pff <- 0.25
qbr <- 0.15
sack_pct <- -0.075
pff_pressure <- 0.1
```

Calculating the SNC grade from PFF data
```{r}
#Calculate pff model
for (player in seq_len(nrow(pff_csv))) {
  player_btt <- btt_pct * pff_csv$btt_rate[player]
  player_twp <- twp_pct * pff_csv$twp_rate[player]
  player_pff <- pff * pff_csv$grades_offense[player]
  player_qbr <- qbr * pff_csv$qb_rating[player]
  player_sackpct <- sack_pct * pff_csv$sack_percent[player]
  player_pffpressure <- pff_pressure * pff_csv$pressure_grade[player]
  player_pffdata <- player_btt + player_twp + player_pff + player_qbr + player_sackpct + player_pffpressure
  pff_csv$player_total_pff[player] <- player_pffdata
}
write.csv(pff_csv, "PFFQBDATA.csv", row.names = FALSE)
```

\section {RBSDM Grade Calculations}

Coefficients and metrics used from RBSDM dataset
```{r}
#RBSDM model coefficients
ay_att <- 0.025
epa_play <- 0.5
epa_cpoe <- 0.4
```

Calculating the SNC grade from RBSDM data
```{r}
#Calculate rbsdm model
for (player in seq_len(nrow(rbsdm_csv))) {
  player_epa <- epa_play * rbsdm_csv$EPA.play[player]
  player_cpoe <- epa_cpoe * rbsdm_csv$EPA.CPOE.composite[player]
  player_airyards <- ay_att * rbsdm_csv$Air.yards[player]
  player_rbsdmdata <- (player_epa + player_cpoe + player_airyards) * 90
  rbsdm_csv$player_total_rbsdm[player] <- player_rbsdmdata
}
write.csv(rbsdm_csv, "RBSDMQBDATA.csv", row.names = FALSE)
```

\section {Combining Data and Plotting Results}

```{r}
#Calculate snc grade
for (player in seq_len(nrow(rbsdm_csv))) {
  player_name <- rbsdm_csv$Player[player]
  player_pffmodel <- pff_csv$player_total_pff[pff_csv$player == player_name]
  player_rbsdmmodel <- rbsdm_csv$player_total_rbsdm[player]
  snc_grade <- player_pffmodel + player_rbsdmmodel
  rbsdm_csv$total_snc_grade[player] <- snc_grade
}

#Plot SNC grades vs PFF grades
plot(pff_csv$grades_offense, rbsdm_csv$total_snc_grade ,xlab = "PFF Grades", ylab = "SNC Grades", main = "Scatter Plot of PFF Grades vs SNC Grades", pch = 20)
abline(lm(rbsdm_csv$total_snc_grade ~ pff_csv$grades_offense), col = "red")
text(pff_csv$grades_offense, rbsdm_csv$total_snc_grade, labels = pff_csv$player, pos = 3, cex = 0.8, col = "black")

#Plot SNC grades vs EPA/play rankings
plot(rbsdm_csv$EPA.play, rbsdm_csv$total_snc_grade ,xlab = "EPA/Play", ylab = "SNC Grades", main = "Scatter Plot of EPA/Play vs SNC Grades", pch = 20)
abline(lm(rbsdm_csv$total_snc_grade ~ rbsdm_csv$EPA.play), col = "red")
text(rbsdm_csv$EPA.play, rbsdm_csv$total_snc_grade, labels = rbsdm_csv$Player, pos = 3, cex = 0.8, col = "black")

write.csv(rbsdm_csv, "RBSDMQBDATA.csv", row.names = FALSE)
```

\section {Conclusions}

Here are my top 32 QB's based on this season alone from my SNC grade (the numbers next to players are their position in the spreadsheet and have no correlation to the players or the grade).
```{r}
rbsdm_csv <- rbsdm_csv[order(rbsdm_csv$total_snc_grade, decreasing = TRUE), ]
top32 <- head(rbsdm_csv[,c("Player", "total_snc_grade")], 32)
print(top32)
```