---
title: "SNC TE Grades"
author: "Gavin Bulthuis"
date: "2024-04-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\section{Load Libraries}
```{r}
install.packages("dplyr")
install.packages("readr")
library(dplyr)
library(readr)
```

\section {Data Loading}
```{r}
#Load data
library(dplyr)
library(readr)

# Load data
pff_csv <- read_csv("PFFTE.csv")
blocking_csv <- read_csv("TEBlocking.csv")

# Combine data by matching rows based on "player" column
combined_data <- left_join(pff_csv, blocking_csv %>% select(player, grades_run_block), by = "player")

# Write to new CSV
write_csv(combined_data, "combined_te_data.csv")

```

\section {Grade Calculations}

Coefficients and metrics used from PFF data set
```{r}
#PFF model coefficients
pff_grade <- combined_data$grades_offense * .30
pff_blocking <- combined_data$grades_run_block * .15
yppr <- combined_data$yprr * 8.5
yac <- combined_data$yards_after_catch_per_reception * 2
yds_game <- (combined_data$yards / combined_data$player_game_count) / 3
qbr_target <- combined_data$targeted_qb_rating / 10
catch_pct <- combined_data$caught_percent / 12
contested_pct <- combined_data$contested_catch_rate / 12
pff_pass_block <- combined_data$grades_pass_block * 0.15
```

Calculating the SNC grade from PFF data
```{r warning=FALSE}
#Calculate pff model
for (player in seq_len(nrow(combined_data))) {
  pff_grade <- combined_data$grades_offense[player] * .45
  pff_blocking <- combined_data$grades_run_block[player] * .25
  yppr <- combined_data$yprr[player] * 12.5
  yac <- combined_data$yards_after_catch_per_reception[player] * 2
  yds_game <- (combined_data$yards[player] / combined_data$player_game_count[player]) / 2
  qbr_target <- combined_data$targeted_qb_rating[player] / 6
  catch_pct <- combined_data$caught_percent[player] / 8
  contested_pct <- combined_data$contested_catch_rate[player] / 7
  pff_pass_block <- combined_data$grades_pass_block[player] * 0.15
  targets_game <- (combined_data$targets / combined_data$player_game_count) * 5
  player_pffdata <- pff_grade + pff_blocking + yprr + yac + yds_game+ qbr_target + catch_pct + contested_pct + pff_pass_block + targets_game
  combined_data$player_total_pff[player] <- player_pffdata * .5
}
write.csv(combined_data, "TEDATA.csv", row.names = FALSE)
```

\section {Conclusions}

Here are my top TE's based on this season alone from my SNC grade (the numbers next to players are their position in the spreadsheet and have no correlation to the players or the grade).
```{r}
pff_csv <- combined_data[order(combined_data$player_total_pff, decreasing = TRUE), ]
top <- head(pff_csv[,c("player", "player_total_pff")], 40)
print(top)
```