---
title: "RB SNC Grades"
author: "Gavin Bulthuis"
date: "2024-02-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here are my SNC RB grades for the 2023 - 2024 NFL season, I will use data from PFF and SumerSports to help in computing the grades.

\section {Data Loading}
Loading data and sorting RB's alphabetically (SumerSports data added to PFF data manually)
```{r}
#Load data
pff_csv <- read.csv("PFFRBDATA.csv")

#Sort players alphabetically
pff_csv <- pff_csv[order(pff_csv$player), ]

```

\section {Grade Calculations}

Coefficients and metrics used from PFF dataset
```{r}
#PFF model coefficients
pff_offense <- 0.4 #approx 20%
yards_att <- 1 #approx 5%
yards_after_contact_att <- 3 #approx 10%
breakaway_pct <- 0.25 #approx 5%
elusive_rating <- 0.1 #approx 5%
receiving_grade <- 0.25 #approx 10%
attempts <- 0.25 #approx 15%
epa_rush <- 10 #approx 20%
yards_created <- 5 #approx 10%
```

Calculating the SNC grade from PFF data
```{r warning=FALSE}
#Calculate pff model
for (player in seq_len(nrow(pff_csv))) {
  player_pff <- pff_offense * pff_csv$grades_offense[player]
  player_yards_att <- yards_att * pff_csv$ypa[player]
  player_yards_after_contact <- yards_after_contact_att * pff_csv$yco_attempt[player]
  player_breakaway <- breakaway_pct * pff_csv$breakaway_percent[player]
  player_elusive <- elusive_rating * pff_csv$elusive_rating[player]
  player_receiving <- receiving_grade * pff_csv$grades_pass_route[player]
  player_attempts <- attempts * pff_csv$attempts
  player_epa <- epa_rush * pff_csv$epa_rush
  player_yards_created <- yards_created * pff_csv$yards_create_att
  player_pffdata <- player_pff + player_yards_att + player_yards_after_contact + player_breakaway + player_elusive + player_receiving + player_attempts + player_epa + player_yards_created
  pff_csv$player_total_pff[player] <- player_pffdata * 0.60
}
write.csv(pff_csv, "PFFQBDATA.csv", row.names = FALSE)
```


\section {Plotting Results}

As you can see below, the well known PFF grade correlates well with my grading formula.
```{r}
#Plot SNC grades vs PFF grades
plot(pff_csv$grades_offense, pff_csv$player_total_pff ,xlab = "PFF Grades", ylab = "SNC Grades", main = "Scatter Plot of PFF Grades vs SNC Grades", pch = 20)
abline(lm(pff_csv$player_total_pff ~ pff_csv$grades_offense), col = "red")
text(pff_csv$grades_offense, pff_csv$player_total_pff, labels = pff_csv$player, pos = 3, cex = 0.8, col = "black")
```

\section {Conclusions}

Here are my top 32 RB's based on this season alone from my SNC grade (the numbers next to players are their position in the spreadsheet and have no correlation to the players or the grade).
```{r}
pff_csv <- pff_csv[order(pff_csv$player_total_pff, decreasing = TRUE), ]
top32 <- head(pff_csv[,c("player", "player_total_pff")], 32)
print(top32)
```
