---
title: "Offensive Tackle Grades"
author: "Gavin Bulthuis"
date: "2024-05-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Here are my SNC OT grades for the 2023 - 2024 NFL season, I will use data from PFF to help in computing the grades.

\section {Data Loading}
Loading data
```{r}
#Load data
pff_csv <- read.csv("otdata.csv")
```

\section {Grade Calculations}

Coefficients and metrics used from PFF dataset
```{r}
#PFF model coefficients
pff_grade = 0.25
pff_pass = 0.175
pff_run = 0.175
pff_tps = 0.125
pff_gap = 0.1
pff_zone = 0.1
pff_eff = 0.075
```

Calculating the SNC grade from PFF data
```{r warning=FALSE}
#Calculate pff model
for (player in seq_len(nrow(pff_csv))) {
  player_pff <- pff_grade * pff_csv$grades_offense[player]
  player_pass <- pff_pass * pff_csv$grades_pass_block[player]
  player_run <- pff_run * pff_csv$grades_run_block[player]
  player_tps <- pff_tps * pff_csv$true_pass[player]
  player_gap <- pff_gap * pff_csv$gap_rblk[player]
  player_zone <- pff_zone * pff_csv$zone_rblk[player]
  player_eff <- pff_eff * pff_csv$pbe[player]
  player_pffdata <- player_pff + player_pass + player_run + player_tps + player_zone + player_gap + pff_eff + 12
  pff_csv$player_total_pff[player] <- player_pffdata
}
write.csv(pff_csv, "OTDATA.csv", row.names = FALSE)
```

\section {Conclusions}

Here are my top OT's based on this season alone from my SNC grade (the numbers next to players are their position in the spreadsheet and have no correlation to the players or the grade).
```{r}
pff_csv <- pff_csv[order(pff_csv$player_total_pff, decreasing = TRUE), ]
top <- head(pff_csv[,c("player", "player_total_pff")], 83)
print(top)
```
